\begin{abstract}
Modern large language models are trained to exhibit consistent behaviours, sometimes referred to as a persona. 
Mechanisms for shaping these personas include weight-space approaches — from broad post-training (RLHF, constitutional AI) to targeted LoRA-based character training, as well as inference-time interventions such as prompting and activation-space steering. 
Weight-space methods are promising for crafting personas, however, it remains an open question whether persona modifications can be decomposed into principled, interpretable trait dimensions that compose predictably. 
We address this by training low-rank LoRA adapters to amplify and suppress personality traits defined by the Big Five (OCEAN) framework, using psychometrically grounded evaluations to measure behavioral change, and compare to activation-space methods. 
We find that these trait-specific adapters act as approximately linear and composable directions in parameter space: scaling a LoRA produces predictable changes in behavior, and linear combinations enable controlled construction of new personas. 
Across a broad range of scales and combinations, these modifications preserve most of the base model’s capabilities. 
To move beyond human-defined traits, we also introduce an unsupervised pipeline for discovering latent behavioral factors from model outputs, which can be interpreted and, in some cases, targeted for control using the same framework.
\todo{Train LoRAs for unsupervised traits or remove (for NeurIPS)}
We further analyze the geometry of learned LoRAs, revealing low-rank structure and systematic relationships between traits. 
Our findings point towards a robust approach to modifying LLM personas in a way that doesn’t noticeably impact performance. 
Further, our results suggest that language model personas can be understood as regions in a structured, partially linear\todo{What does it mean that it's partially linear?} weight space, providing a principled foundation for persona analysis and control that complements existing activation-space and fine-tuning approaches.
\end{abstract}
