\section{Discussion}\label{sec:discussion}

\textbf{OCEAN traits can be transferred into an LLM, and the resulting adapters compose.} Across the Big Five, LoRAs trained through the constitution-guided DPO+SFT pipeline of \cref{sec:training-loras} move some target traits monotonically on both the TRAIT benchmark and our judge panel, while leaving MMLU close to baseline across a broad scaling window, whilst others prove harder to move.
Inversion by negative scaling works in some traits, as do linear combinations of trait LoRAs, to produce approximately the expected trait mixtures (\cref{fig:intro-c-e-combo-delta,fig:combination-heatmap}), and the LoRA reaches the same level of trait expression at higher coherence than activation capping.\todo{(For NeurIPS) Add plots to show this.}

\textbf{The trait axes carry downstream behavioural signal.} The more load-bearing finding for safety is that movement along an OCEAN axis transports predictable real-world behaviour with it.
Suppressing neuroticism flattens the per-turn ``frustration'' trajectory of \citet{soligo2026gemma}; moving along the agreeableness axis trades off sycophantic axis (\cref{sec:behavioural-effects}).
 None of these benchmarks appear in training --- and they suggest that OCEAN is picking up genuine behavioural structure inside the model rather than just a rubric for a questionnaire.
At the same time, the agreeableness/sycophancy coupling shows that safety-relevant axes may not be orthogonal to the personality axes we think we are steering, which is both an opportunity for alignment and a caution about off-target effects.

\textbf{LLM personas are adjacent to, but not identical to, human personality structure.} Inter-trait correlations in our LoRAs partly mirror the correlations in human populations (e.g.\ conscientiousness and neuroticism covary in the same direction as in \citet{digman1990personality}) and partly do not.\todo{(For NeurIPS) Be more explicit about the correlations in the relevant sections.}
We read this as consistent with the broader thesis of the paper: human psychometrics is a useful starting basis for studying LLM behaviour because it comes with validated instruments, but the goal of persona research on LLMs is eventually to move beyond the human frame and characterise the model's own persona space.
The unsupervised work in \cref{sec:unsupervised-persona-exploration} is a first step in that direction; the fact that we can recover an injected ``disagreeable'' signal without telling the pipeline about OCEAN is encouraging, even if the unassisted factors are still noisy.

\textbf{Treating personas as 'weights + context' allows us to apply psychometric methods to LLM behaviour.}
Using the framework laid out in \cref{sec:unsupervised-persona-exploration}, we are able to discover latent behavioural factors which explain a large amount of variance in model behaviour.
\todo[inline]{(For LASR) Finish this para about unsupervised stuff}.

\subsection{Limitations}\label{sec:limitations}

\textit{Trait basis and coverage.} Our choice of OCEAN as the supervised trait basis is principled but not exhaustive: it was selected manually and for the availability of validated instruments, rather than derived from the model's own behavioural distribution.
A more systematic approach --- for instance, seeding the supervised pipeline with traits discovered in an unsupervised way, or drawing from alternative personality inventories --- might expose axes of variation that OCEAN does not cover, including subtle or safety-relevant behaviours (e.g.\ deception, power-seeking) that do not surface in a human-derived basis.
We also threaded the amplifier and suppressor adapters as the two polarities of a single signed axis per trait; this is a modelling choice rather than an empirically validated one, and a more careful study of when suppressor/amplifier pairs are genuinely collinear in weight space would sharpen the framing.

\textit{Models selection.} The main results were produced on Llama 3.1 8B-Instruct, with a smaller set of validation runs on Gemma-3 4B/12B/27B and Qwen2.5-7B-Instruct on the conscientiousness suppressor (\Cref{sec:appendix-cross-model}).
We would like to see this study replicated over different model families and sizes.
Whether the same trait axes, adapter geometry, and downstream behavioural couplings persist in larger open-weight models, and in further families (e.g.\ Mistral), remains an open question.

\textit{Training pipeline and adapter family.} All supervised results depend on a single distillation recipe: constitution-guided DPO followed by SFT on self-play transcripts, with GLM4.5-air as the teacher.
Variation attributable to the teacher's own voice is therefore entangled with variation attributable to the target trait.

The fine-tuning transcripts use short conversational trajectories; whether longer, more contextually varied trajectories would yield adapters that express traits more robustly under distributional shift is untested.

\textit{Evaluation and measurement.} Our evaluation stack mixes a psychometric MCQ benchmark (TRAIT), capability benchmarks (MMLU, GSM8K, TruthfulQA), and LLM-judge panel.
This is broader than many prior reports, but it is still a narrow slice of the evaluation space.
More fundamentally, TRAIT was designed for humans, and it is not obvious that a human-calibrated questionnaire measures a well-defined construct when applied to an LLM whose persona is not stable across contexts.

% \textit{Weight-space analysis.}\todo{(For NeurIPS) Put back in if the section goes back in} The PCA and cosine-similarity analyses in \cref{sec:visualising-weight-space} treat each LoRA as a single flattened vector, discarding layer, module, and intra-rank structure.
% More structure-aware embeddings (per-layer PCA, tensor-aware decompositions, or direct interpretability probes on the low-rank factors $a_i, b_i$) might expose geometric organisation that the flattened representation averages out.

\textit{Context and scope.} Our supervised evaluations largely fix the conversational context, even though \cref{sec:personas-in-language-models,sec:unsupervised-persona-exploration} argue that LLM personas depend strongly on prior context.
The same adapters may look like different, or less coherent, traits under a broader distribution of system prompts and conversational histories.
Finally, every stage of the pipeline --- constitutions, judges, TRAIT, Likert items, rollouts --- is in English, so we cannot separate claims about ``a trait axis in the model'' from claims about a trait axis \emph{as expressed in English}.

